Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
split init contraints into init and input

Furthermore, it is practically relevant to consider constraints on the input
signal $u_{k}$ and bounds on the initial states $x_0$,
which we assume have given bounds. %%  $\overline{u}$, $\underline{u}$
%% and $\overline{x_0}$, $\underline{x_0}$, respectively.
We refer to these constraints as $\phi_{init}$: \todo{input constraints should not be called 'init'}
$$\phi_{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} 
\wedge \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$$  
In the first case, this means that the control input saturates in view of
physical constraints.

>>>>

Furthermore, it is practically relevant to consider the 
constraints $\phi_{init}$ on the input
signal $u_{k}$ and $\phi_{input}$ on the initial states $x_0$,
which we assume have given bounds:
$\phi_{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
$\phi_{input} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
In the first case, this means that the control input saturates in view of
physical constraints.
